Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
small fixes
add Abani Patra's talk

\item \textbf{Abani Patra, Hossein Aghakhani, Nikolay Simakov, Matthew D. Jones
and Tevfik Kosar: \textit{Integrating New Functionality Using Smart Interfaces to
Improve Productivity of Legacy Tools}}

@@

\item \textbf{Alice Allen: \textit{We’re giving away the store! (Merchandise not
included)}}

>>>>

\item \textbf{Abani Patra, Hossein Aghakhani, Nikolay Simakov, Matthew D. Jones
and Tevfik Kosar: \textit{Integrating New Functionality Using Smart Interfaces to
Improve Productivity of Legacy Tools}}
Abani Patra presented an example how the community using Titan2d, a Geoflow
Simulation Software, increased the productivity of their tools by improving
both code and data layout. Main obstacles in this change were the non-existence
of a common version control system for the source code, coupled with multiple
versions of the same code base, the fixed format of input files, that many
input values used to be set as compilation flags, and that the internal data
layout was not suitable for modern technologies (vectorization, accelerators).
The approach of the Titan2d developers included reinforcing the code structure
using a multiple laters of Python and C++, and a redesign of the data layout to
be better suitable for modern CPUs and accelerators.

@@

\item \textbf{Alice Allen: \textit{We're giving away the store! (Merchandise not
included)}}
